\section{\mysidestyle Work Experience}
\textbf{Data Scientist}, Peoplefund Company Incorporated \hfill \textsl{Sep 2022 - Jul 2023}\\
Data Strategy Team \hfill Seoul, South Korea

\begin{list2}
    \item {Optimized the loan approval strategy model, cutting runtime from 3 days to 10 minutes, elevating the product into a viable solution for enterprise-level lenders.}
    \item {Designed and implemented a new loan performance prediction model, reducing MAPE from 41\% to 6\%.}
    \item {Defined the comprehensive objective function and completed code architecture for a loan profit optimization model. Its backtesting results conservatively estimate a 5-18\% increase in revenue.}
    \item {Led collaboration with engineering and business teams to incorporate modern data science tools, such as Superset, MLFlow, and others, streamlining operations and standardizing documentation.}
    \item {Deployed proof-of-concept products, supplying full-stack codes to support engineering teams in further development.}
\end{list2}

\textbf{Data Scientist}, Voithru Corporation \hfill \textsl{Nov 2021 - Sep 2022}\\
Data Team \hfill Seoul, South Korea

\begin{list2}
    \item {Launched and managed the company's first-ever fraud detection system based on freelancer behavior logs on the company platform, detecting 1000+ fraudulent translations (5-10\% of total) per month.}
    \item {Developed a novel ranking system to oversee 1,700+ freelancers, integrating 12+ performance metrics derived from feedback by product and quality management teams.}
    \item {Deployed the first deep learning subtitle categorization model with an approximately 90\% accuracy rate to provide insights for the quality management team and the fraud detection system.}
    \item {Built and maintained Apache Superset dashboards to visualize freelancer performances and statistics.}
    \item {Proposed a machine-translation-assisted translation experiment design to improve productivity by over 20\%, and kickstarted the platform development.}
    \item {Implemented a bioinformatics algorithm to automate audio-subtitle matching. Improved the in-house system's time efficiency by three orders of magnitude while drastically improving the accuracy.}
\end{list2}